Exceedance probability comparison for the simplified Naomi model

### 2023-05-16 src/naomi-simple_exceedance/exceedance.Rmd
Update exceedance case-study with figures that can go into manuscript #35

plot1 <- ggplot(df_wide_second90, aes(x = tmbstan, y = TMB, col = sex)) +
  geom_point(alpha = 0.3) +
  scale_color_manual(values = c("#E69F00", "#F0E442")) +
  geom_abline(slope = 1, intercept = 0, col = "#CC79A7", linetype = "dashed") +
  labs(title = "Probability of at least 81% ART coverage in strata", col = "Sex") +
  theme_minimal() +
  theme(legend.position = "bottom")

plot2 <- ggplot(df_wide_second90, aes(x = tmbstan, y = aghq, col = sex)) +
  geom_point(alpha = 0.3) +
  scale_color_manual(values = c("#E69F00", "#F0E442")) +
  geom_abline(slope = 1, intercept = 0, col = "#CC79A7", linetype = "dashed") +
  guides(col = "none") +
  theme_minimal()

@@

plot1 <- ggplot(df_wide_1inc, aes(x = tmbstan, y = TMB)) +
  geom_point(alpha = 0.3) +
  geom_abline(slope = 1, intercept = 0, col = "#CC79A7", linetype = "dashed") +
  labs(title = "Probability of at least 1% incidence in strata") +
  theme_minimal()

@@

>>>>

plot1 <- ggplot(df_wide_second90, aes(x = tmbstan, y = TMB, col = sex)) +
  geom_point(alpha = 0.3) +
  scale_color_manual(values = c("#56B4E9","#009E73")) +
  geom_abline(slope = 1, intercept = 0, col = "#CC79A7", linetype = "dashed") +
  labs(subtitle = "Probability of greater than 81% ART coverage in strata", col = "Sex") +
  guides(col = "none") +
  labs(x = "NUTS", y = "TMB") +
  theme_minimal()

plot2 <- ggplot(df_wide_second90, aes(x = tmbstan, y = aghq, col = sex)) +
  geom_point(alpha = 0.3) +
  scale_colour_manual(values = c("#56B4E9","#009E73"), labels = c("Female", "Male")) +
  geom_abline(slope = 1, intercept = 0, col = "#CC79A7", linetype = "dashed") +
  guides(colour = guide_legend(override.aes = list(alpha = 1))) +
  labs(x = "NUTS", y = "PCA-AGHQ", col = "Sex") +
  theme_minimal()

pdf("second90.pdf", h = 4, w = 6.25)

dev.off()

@@

plot1 <- ggplot(df_wide_1inc, aes(x = tmbstan, y = TMB)) +
  geom_point(alpha = 0.3) +
  geom_abline(slope = 1, intercept = 0, col = "#CC79A7", linetype = "dashed") +
  labs(subtitle = "Probability of at least 1% incidence in strata") +
  theme_minimal()

@@

pdf("1inc.pdf", h = 4, w = 6.25)

dev.off()
